% THIS DOCUMENT IS FOLLOWS THE VOLERE TEMPLATE BY Suzanne Robertson and James Robertson
% ONLY THE SECTION HEADINGS ARE PROVIDED
%
% Initial draft from https://github.com/Dieblich/volere
%
% Risks are removed because they are covered by the Hazard Analysis
\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
      colorlinks=true,      % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
\usepackage{enumitem}
\newcommand{\lips}{\textit{Insert your content here.}}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Software Requirements Specification for \progname: subtitle describing software} 
\author{\authname}
\date{\today}
	
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

~\newpage

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\textbf{Date}} & {\textbf{Version}} & {\textbf{Notes}}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\\

~\newpage
\section{Purpose of the Project}
\subsection{User Business}
\lips
\subsection{Goals of the Project}
\lips
\section{Stakeholders}
\subsection{Client}
\lips
\subsection{Customer}
\lips
\subsection{Other Stakeholders}
\lips
\subsection{Hands-On Users of the Project}
\lips
\subsection{Personas}
\lips
\subsection{Priorities Assigned to Users}
\lips
\subsection{User Participation}
\lips
\subsection{Maintenance Users and Service Technicians}
\lips

\section{Mandated Constraints}
\subsection{Solution Constraints}
\lips
\subsection{Implementation Environment of the Current System}
\lips
\subsection{Partner or Collaborative Applications}
\lips
\subsection{Off-the-Shelf Software}
\lips
\subsection{Anticipated Workplace Environment}
\lips
\subsection{Schedule Constraints}
\lips
\subsection{Budget Constraints}
\lips
\subsection{Enterprise Constraints}
\lips

\section{Naming Conventions and Terminology}
\subsection{Glossary of All Terms, Including Acronyms, Used by Stakeholders
involved in the Project}
\lips

\section{Relevant Facts And Assumptions}
\subsection{Relevant Facts}
\lips
\subsection{Business Rules}
\lips
\subsection{Assumptions}
\lips

\section{The Scope of the Work}
\subsection{The Current Situation}
\lips
\subsection{The Context of the Work}
\lips
\subsection{Work Partitioning}
\lips
\subsection{Specifying a Business Use Case (BUC)}
\lips

\section{Business Data Model and Data Dictionary}
\subsection{Business Data Model}
\lips
\subsection{Data Dictionary}
\lips

\section{The Scope of the Product}
\subsection{Product Boundary}
\lips
\subsection{Product Use Case Table}
\lips
\subsection{Individual Product Use Cases (PUC's)}
\lips

\section{Functional Requirements}
\subsection{Functional Requirements}
\lips

\section{Look and Feel Requirements}
\subsection{Appearance Requirements}
\lips
\subsection{Style Requirements}
\lips

\section{Usability and Humanity Requirements}
\subsection{Ease of Use Requirements}
\lips
\subsection{Personalization and Internationalization Requirements}
\lips
\subsection{Learning Requirements}
\lips
\subsection{Understandability and Politeness Requirements}
\lips
\subsection{Accessibility Requirements}
\lips

\section{Performance Requirements}
\subsection{Speed and Latency Requirements}
\lips
\subsection{Safety-Critical Requirements}
\lips
\subsection{Precision or Accuracy Requirements}
\lips
\subsection{Robustness or Fault-Tolerance Requirements}
\lips
\subsection{Capacity Requirements}
\lips
\subsection{Scalability or Extensibility Requirements}
\lips
\subsection{Longevity Requirements}
\lips

\section{Operational and Environmental Requirements}
\subsection{Expected Physical Environment}

\begin{enumerate}[label=\thesubsection-\arabic*]
\item The tool is a web-based application that will be used mainly by our team, supervisors, and potentially other researchers or domain experts.
\item It is expected to run on a standard desktop or laptop computer with a reliable internet connection, in a normal indoor setting such as an office, lab, or home workspace.
\item No specialized hardware or rugged equipment is required. A keyboard, mouse, or touchpad, and a modern web browser (e.g., Chrome, Firefox, Edge) are sufficient.
\end{enumerate}

\subsection{Wider Environment Requirements}
\begin{enumerate}[label=\thesubsection-\arabic*]
\item The application depends on a stable internet connection for retrieving data from public repositories (e.g., GitHub) and for loading the hosted web interface if deployed to the cloud.
\item It does not rely on any dedicated on-premises hardware.
\item The tool should work on the latest two to three major versions of common browsers such as Chrome, Firefox, and Edge. No special environmental conditions (lighting, noise, temperature) are expected to affect usability.
\end{enumerate}
\subsection{Requirements for Interfacing with Adjacent Systems}
The tool must be able to communicate with a few external systems and internal components to collect, store, and visualize data.

\begin{enumerate}[label=\thesubsection-\arabic*]

  \item Public Repository APIs (e.g., GitHub API): The tool must communicate with external repository services to automatically collect information about the selected neural-network libraries. For example, it needs to retrieve details such as how often the code is updated, the number of open or closed issues and pull requests, and the main programming languages used. This data will help evaluate qualities like maintainability, transparency, and overall project activity. The information must be received in a standard machine-readable format (e.g., JSON over HTTPS) whenever a user triggers a scan or during scheduled updates.

  \item Database (MySQL): The backend must store scores, rankings, and evidence collected from repositories.

  \item Visualization Component: The frontend must render charts and comparisons (e.g., using Chart.js) from the data served by the backend.

  \item All connections must use standard web technologies (HTTP/HTTPS, JSON) and require only basic authentication methods such as API tokens for secure access to external repository APIs.

\end{enumerate}

\subsection{Productization Requirements}
The tool will be delivered as an open-source web application hosted in the team’s public GitHub repository.
\begin{enumerate}[label=\thesubsection-\arabic*]
\item A clear README file must explain how to set up the backend (Python + Flask) and the frontend (React) using common package managers such as pip and npm.
\item For developers running the tool locally, the repository must include a requirements.txt file for Python packages and a database schema file so they can create the required tables.
\item When deployed on a cloud platform such as AWS or Google Cloud, users must be able to access the tool directly through a web URL without installing anything.
\item The application must also provide options to export results in formats such as CSV for data tables and PNG/PDF for visualizations.
\end{enumerate}
\subsection{Release Requirements}
\begin{enumerate}[label=\thesubsection-\arabic*]
\item The project should follow the official capstone timeline: an internal test release before the Proof-of-Concept (PoC) demonstration in \textbf{November}, a Revision~0 Demonstration in \textbf{Weeks~18--19}, and the Final Release (Revision~1) at \textbf{Week~26} along with the research paper and final dataset.
\item The Final Release (Revision 1) must incorporate feedback collected during the Revision 0 Demonstration, including usability improvements, bug fixes, and supervisor/TA-requested changes.
\item All releases must be published as GitHub Releases and include a short changelog describing the changes in each version.

  \item Releases must use a clear, descriptive version tag such as the \texttt{MAJOR.MINOR.PATCH} format (or an equally descriptive format):
    \begin{itemize}
        \item \textbf{MAJOR:} Increased only when a change breaks backward compatibility (e.g., a database schema change that makes older data unusable).
        \item \textbf{MINOR:} Increased when adding new features that remain fully compatible with previous versions.
        \item \textbf{PATCH:} Increased for bug fixes or small improvements that do not affect existing features.
    \end{itemize}

  Example version tags:
    \begin{itemize}
        \item \texttt{v0.1.0} → first working prototype for the Revision~0 Demonstration
        \item \texttt{v0.2.0} → adds a new feature such as exporting the table to a CSV file
        \item \texttt{v0.2.1} → fixes a small bug in the export feature (patch)
        \item \texttt{v1.0.0} → stable Final Release for Revision~1
    \end{itemize}
\end{enumerate}
\section{Maintainability and Support Requirements}
\subsection{Maintenance Requirements}
The tool is an open-source web application that will need occasional updates to fix bugs and to adapt if external APIs change.
\begin{enumerate}[label=\thesubsection-\arabic*]
\item All code must follow the project’s coding standards (PEP 8 for the Python backend; React + TypeScript style guide for the frontend).
\item Automated tools (such as Black, Flake8, and Pylint) must remain part of the workflow so new contributors can easily read and update the code.
\item Unit tests must be written for all new features and bug fixes. Developers should also run basic integration tests to make sure the full pipeline (API → database → visualization) still works after changes.
\item Test coverage must be tracked and reported to ensure that critical parts of the backend are being tested.
\item All Python and frontend packages must be listed in requirements.txt and package.json, with pinned versions so the same build can be reproduced.
\item The dependency list must be reviewed and updated at least once each semester to keep it current and secure.
\item Any changes to the dataset made through the interactive data table must be logged with a timestamp and the username so there is always a clear audit trail.
\item Most routine fixes, such as small UI tweaks or bug fixes, should be finished within a couple of days. Larger updates, such as adding a new metric or a new visualization, are expected to take about one to two weeks.
\end{enumerate}
\subsection{Supportability Requirements}
The tool is intended to be mostly self-supporting since it will be used primarily by our team, the supervisors, and potentially other researchers in the future.
\begin{enumerate}[label=\thesubsection-\arabic*]
\item The README file must include step-by-step instructions so that a new developer can set up the backend (Flask + MySQL) and frontend (React) locally, or deploy it to a cloud platform (such as AWS or Google Cloud), in a consistent and repeatable way. A new developer should be able to follow these instructions and have the application running within about two hours.
\item The repository must always include an up-to-date guide for installation, setup, the data-collection workflow, using the interactive data table, visualization, and exporting results.
\item The backend must include logging to record API failures (such as rate-limit errors or unexpected data formats), database issues, and runtime exceptions so that maintainers can troubleshoot problems quickly.
\item Users should use the GitHub Issues page to report bugs or ask questions. No printed manual will be needed; all documentation will remain online in the repository.
\end{enumerate}
\subsection{Adaptability Requirements}
\begin{enumerate}[label=\thesubsection-\arabic*]
\item The tool must remain flexible so it can grow with the project and adapt to future needs.
\item The MySQL database must be set up so that if a new quality criterion needs to be tracked, it can be added by creating a new column, updating the data-collection script, and adjusting the UI without having to redesign the whole system.
\item The data-collection module must allow new data sources (for example, another code-hosting site or a different metrics service) to be added with minimal extra code and without disrupting the existing GitHub integration.
\item The tool must be able to run on standard operating systems(Windows, macOS, and Linux) by using widely supported technologies (such as Python, Node.js, and MySQL), and by avoiding any system-specific code.
\item The system must be designed in a modular way so that parts like data collection, storage, and visualization remain separate. This makes it easier to add new features or update one part without affecting the rest of the tool.
\end{enumerate}
\section{Security Requirements}
\subsection{Access Requirements}


\begin{enumerate}[label=\thesubsection-\arabic*]

  \item The tool must be open for anyone to view results, but only approved team members or domain experts may modify the data.

  \item The system must support two user roles:
    \begin{itemize}
        \item \textbf{Viewer:} Can view all interactive data tables that list the libraries, their scores, and rankings, along with all visualizations.
        \item \textbf{Contributor:} Has all Viewer permissions plus the ability to edit data in the interactive table.
    \end{itemize}

  \item Editing or any other administrative actions must be available only to logged-in users with the \textbf{Contributor} role.

  \item User roles (Viewer / Contributor) must be assigned and updated correctly at signup or by an admin so that permissions always reflect the intended access level.

  \item The system must display clear error messages for login failures (e.g., invalid credentials, network errors) and provide a secure way for users to recover or reset their account credentials.

  \item API credentials such as keys or tokens for external services (e.g., repository APIs) must be stored securely outside the source code (e.g., in environment variables) and must never be exposed in the frontend or version control.

\end{enumerate}

\subsection{Integrity Requirements}
\begin{enumerate}[label=\thesubsection-\arabic*]
\item To ensure the accuracy and reliability of the collected data, all manually entered information into the interactive table must be checked before it is saved. For example, numbers must fall within valid ranges, and text must be cleaned so that it cannot be treated as code or scripts.
\item The database must include safeguards so that if two users edit the same record at the same time, no changes are lost or overwritten.
\item The system must detect simultaneous edits and either block one save or notify the users to resolve the conflict.
\item When automated data updates conflict with a user’s manual edits (if any are updated automatically), the system must warn the user or request confirmation before replacing existing data.
\item The system must also store the raw evidence, calculated scores, and final rankings in separate fields so that the original data and results cannot be accidentally modified.
\item Publishing visualizations must not occur at the same time as data edits or automated refreshes. The system must either block publishing or enforce downtime until updates are complete.
\item If an export (e.g., CSV, PNG) fails or produces a corrupted file, the tool must alert the user and allow them to retry the download.
\end{enumerate}
\subsection{Privacy Requirements}
The tool mainly works with open-source repository data, so there is very little personal data involved.
\begin{enumerate}[label=\thesubsection-\arabic*]
\item If basic user details are collected for login (such as name or email), they must be kept private and stored securely using widely accepted security standards.
\item User passwords must be stored only in hashed form using a secure one-way hashing algorithm so that the actual password is never saved.
\end{enumerate}
No other personal or confidential information will be collected or stored.
\subsection{Audit Requirements}
\begin{enumerate}[label=\thesubsection-\arabic*]
\item The system must keep a record of all important activity for accountability and troubleshooting. Every time a Contributor adds, edits, or deletes data in the interactive table, the system must save a log entry showing the user’s ID, the time of the action, the type of action, and the fields that were changed.
\item The system must also log key events such as login attempts (successful and failed), scheduled API-collection runs, and major errors so that they can be reviewed later.
\item Access to these logs must be restricted to authorized project admins only.
\end{enumerate}
\subsection{Immunity Requirements}
\begin{enumerate}[label=\thesubsection-\arabic*]
\item The backend must prevent SQL-injection attacks by using the safe query methods provided by the database library instead of building raw SQL strings with user input.
\item The frontend must display any text entered by users as plain text only and never allow it to run as code. For example, React’s built-in escaping already takes care of this.
\item The automated data-collection scripts must respect the rate limits of external repository APIs (e.g., GitHub). If a limit is reached, the scripts should pause and retry later rather than keep sending requests and risk overloading the service.
\item All Python and React libraries must be kept up to date, so the project does not rely on outdated packages with known security issues. There should also be a tool in place to regularly check for known vulnerabilities in these libraries, such as GitHub Dependabot.
\end{enumerate}

\section{Cultural Requirements}
\subsection{Cultural Requirements}
Since the tool will be shared mostly in an academic and research setting, we just need to make sure the interface stays clear, neutral, and easy to understand for anyone who uses it later.
\begin{enumerate}[label=\thesubsection-\arabic*]
\item \textbf{Language:} All text in the user interface and documentation must be in plain English. We should avoid using region-specific jargon so that future collaborators from outside McMaster can understand it easily.
\item \textbf{Dates and Numbers:} Dates must be displayed in a clear standard format such as ISO 8601 (YYYY-MM-DD) so they’re unambiguous for anyone who uses the tool. Numbers must use a consistent style (for example, decimal point for fractions and thousands separated by commas).
\item \textbf{Neutral Design:} Colours, labels, and icons must stay neutral and must not include any symbols or words that could carry unintended cultural or political meaning.
\item \textbf{Open-Source Norms:} The repository must include a license notice and simple contribution guidelines to match common open-source practice.
\end{enumerate}
\section{Compliance Requirements}
\subsection{Legal Requirements}
\begin{enumerate}[label=\thesubsection-\arabic*]
\item The tool must include a copyright notice covering the code and documentation produced by the team.
\item It must be distributed under an appropriate open-source license so that others can reuse it under clearly defined terms.
\item Users of the tool or any data generated by it are required to provide proper citation or acknowledgement when they use it in their own work.
\end{enumerate}
\subsection{Standards Compliance Requirements}
N/A

\section{Open Issues}
\lips

\section{Off-the-Shelf Solutions}
\subsection{Ready-Made Products}
\lips
\subsection{Reusable Components}
\lips
\subsection{Products That Can Be Copied}
\lips

\section{New Problems}
\subsection{Effects on the Current Environment}
\lips
\subsection{Effects on the Installed Systems}
\lips
\subsection{Potential User Problems}
\lips
\subsection{Limitations in the Anticipated Implementation Environment That May
Inhibit the New Product}
\lips
\subsection{Follow-Up Problems}
\lips

\section{Tasks}
\subsection{Project Planning}
\lips
\subsection{Planning of the Development Phases}
\lips

\section{Migration to the New Product}
\subsection{Requirements for Migration to the New Product}
\lips
\subsection{Data That Has to be Modified or Translated for the New System}
\lips

\section{Costs}
\lips
\section{User Documentation and Training}
\subsection{User Documentation Requirements}
\lips
\subsection{Training Requirements}
\lips

\section{Waiting Room}
\lips

\section{Ideas for Solution}
\lips

\newpage{}
\section*{Appendix --- Reflection}

\input{../Reflection.tex}

\input{../SRS_Reflection.tex}

\end{document}